### 2015-07-28 Docs/introduction/introduction.tex
update paper list + add notes on what portions of the algorithm are described in any appendices

\noindent \maestro\ was developed initially for modeling the convecting
phase in a white dwarf preceding the ignition of a Type Ia supernovae.
As such, we needed to incorporate the compressibility effects due to
large-scale stratification in the star.  The method closest in spirit
to \maestro\ is the pseudo-incompressible method of
Durran~\cite{durran}, developed for terrestrial atmospheric flows
(assuming an ideal gas).  Part of the complexity of the equations in
\maestro\ stems from the need to descibe a general equation of state.
Additionally, since reactions can significantly alter the hydrostatic
structure of a star, we incorporated extensions that capture the
expansion of the background state~\cite{almgren:2000}.  The low Mach
number equations for stellar flows were developed in a series of
papers leading up to the first application to this problem:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics,} A. S. Almgren, J. B. Bell, 
  C. A. Rendleman, \& M. Zingale 2006, ApJ, 637, 922 (henceforth
  paper I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution,} A. S. Almgren, J. B. Bell, C. A. Rendleman, \& M. Zingale
  2006, ApJ, 649, 927 (henceforth paper II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions,}
  A. S. Almgren, J. B. Bell, A. Nonaka, \& M. Zingale
  2008, ApJ, 684, 449 (henceforth paper III)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. IV. White Dwarf Convection,}
  M. Zingale, A. S. Almgren, J. B. Bell, A. Nonaka, \& S. E. Woosley
  2009, ApJ, 704, 196 (henceforth paper IV)
\end{itemize}

@@

\noindent We have several papers that describe applications of the
method to Type Ia supernovae, X-ray bursts, and stellar evolution:
\begin{itemize}
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2011,
  ApJ, 728, 118 (henceforth ``the XRB paper'')

@@

\item {\it Comparisons of Two- and Three-Dimensional Convection in Type I X-ray Bursts} 
M.~Zingale, C.~M.~Malone, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell 
submitted to ApJL.

>>>>

\noindent \maestro\ was developed initially for modeling the convecting
phase in a white dwarf preceding the ignition of a Type Ia supernovae.
As such, we needed to incorporate the compressibility effects due to
large-scale stratification in the star.  The method closest in spirit
to \maestro\ is the pseudo-incompressible method of
Durran~\cite{durran}, developed for terrestrial atmospheric flows
(assuming an ideal gas).  Part of the complexity of the equations in
\maestro\ stems from the need to descibe a general equation of state.
Additionally, since reactions can significantly alter the hydrostatic
structure of a star, we incorporated extensions that capture the
expansion of the background state~\cite{almgren:2000}.  The low Mach
number equations for stellar flows were developed in a series of
papers leading up to the first application to this problem:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics,} A. S. Almgren, J. B. Bell, 
  C. A. Rendleman, \& M. Zingale 2006, ApJ, 637, 922 (henceforth
  paper I)

\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution,} A. S. Almgren, J. B. Bell, C. A. Rendleman, \& M. Zingale
  2006, ApJ, 649, 927 (henceforth paper II)

\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions,}
  A. S. Almgren, J. B. Bell, A. Nonaka, \& M. Zingale
  2008, ApJ, 684, 449 (henceforth paper III)

\item {\em Low Mach Number Modeling of Type Ia Supernovae. IV. White Dwarf Convection,}
  M. Zingale, A. S. Almgren, J. B. Bell, A. Nonaka, \& S. E. Woosley
  2009, ApJ, 704, 196 (henceforth paper IV)
\end{itemize}

@@

\noindent We have several papers that describe applications of the
method to Type Ia supernovae, X-ray bursts, and stellar evolution.  Some of these
papers have appendices that describe enhancements to the code---these are noted
below.
\begin{itemize}
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2011,
  ApJ, 728, 118 (henceforth ``the XRB paper'')

  This introduces the thermal diffusion portion of the \maestro\ algorithm.

@@

\item {\it Comparisons of Two- and Three-Dimensional Convection in
  Type I X-ray Bursts} M.~Zingale, C.~M.~Malone, A.~Nonaka,
  A.~S.~Almgren, \& J.~B.~Bell 2015, ApJ, 807, 60.

  This has an appendix that describes the Godunov state construction in more
  detail than previous papers.

\item {\it Low Mach Number Modeling of Convection in Helium Shells on
  Sub-Chandrasekhar White Dwarfs II: Bulk Properties of Simple Models,
} A.~M.~Jacobs, M.~Zingale, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell
  2015, submitted to ApJ

  This has an appendix that shows some test problems for the new energy 
  formulation in \maestro.
